A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-15 ms.Rmd
rough go at an Abstract...

# ABSTRACT

TBD

>>>>

# ABSTRACT
Understanding species' responses to urbanization is critical to the conservation of urban biodiversity. Previous work assessing ecological and life history traits that are associated with urban birds has elucidated differing and contrasting patterns for a wide variety of traits. Much of this work has relied on a priori grouping of species into discrete groups (e.g., urban avoiders, exploiters, and adapters or even binary presence/absence in urban areas), and has been spatially and/or temporally limited. Here, we provide a novel and easily adapted methodology which uses a continuous urbanization index to assess which ecological and life history traits most influence a species' ability to be found in urban environments. A continuous measure of urbanization is critical as it fully accounts for the inherent differences in species' responses to urban environments. We further expand on previous studies by incorporating a total of 477 species in our analyses, a number far greater than similar studies, to the best of our knowledge. We find a significant phylogenetic effect of our urbanization index and thus account for the non-linear relationships among species in our modelling. Niche breadth, as measured by various types of generalism, and clutch size are among the most important predictors of urbanization. We also find that residual brain mass is a critical predictor within our phylogenetic models, suggesting that those species within a clade which have the largest relative brain size are most readily adapting to urban development. Urbanization is selecting against specialists, granivores, and insectivores. These results have important implications for aiding the preservation and persistence of urban avian biodiversity.
